\subsection{Dimensionality}
\paragraph{The Curse of Dimensionality} % (fold)
\label{par:paragraph_name}
`The Curse of Dimensionality' refers to the set of problems that arise due to high dimensional feature spaces. As the number of features one deals with increases, problems occur when trying to apply standard machine learning methods. The first is that training and testing speeds can be prohibitive.  A more important problem is that as the number of features increases, the variation among pairwise distances between points decreases, leading to less discrimination between regions of feature space and less reliable results. Beyer et. al. stated the problem that as dimensionality increases the distance of the nearest neighbor to the farthest neighbor becomes small ~\cite{beyer1999nearest}. They show this by proving that the distance to the farthest point converges in probability to the closest point multiplied by a factor of $(1+\epsilon)$ for all $\epsilon > 0$, formally:
\begin{equation}
	\lim_{m\rightarrow \infty} P[DMAX_m \le (1+\epsilon)DMIN_m]=1
\end{equation}
% paragraph paragraph_name (end)
\paragraph{Johnson-Lindenstauss} % (fold)
\label{par:johnson_lindenstauss}
The curse of dimensionality suggests that we may benefit from decreasing data dimensionality if we can compress it a lower dimensional space while maintaing its important, discriminative characteristics. The summarization of a feature space into a lower dimensional space is called dimensionality reduction. Johnson and Lindenstauss  showed in a well-used lemma that a set of points can be projected into a smaller dimensional space from a larger one such that the points' pairwise distances are nearly preserved ~\cite{johnson1984extensions}. Formally, there exists a mapping $f$ such that $:\mathbb{R}^n \rightarrow \mathbb{R}^k$ with probability $1-n^{-\beta}$ ,  $\forall u,v \in P$:
\begin{equation}
	(1 - \epsilon)||u - v||^2 \le ||f(u)-f(v)||^2 \le (1+\epsilon)||u-v||^2
\end{equation}  ~\cite{achlioptas2001database} The two methods that were used in this project for performing dimensionality reduction are Principal Component Analysis (PCA) using Singular Value Decomposition (SVD) as well the method of random projections.
% paragraph johnson_lindenstauss (end)
\paragraph{Singular Value Decomposition} % (fold)
\label{par:singular_value_decomposition}
The method of Singular Value Decomposition decomposes a data matrix to the form $A = U \Sigma V^T$, where 
if $A$ is of size $m \times n$, $U$ is an orthogonal matrix of size $m \times p$, $\Sigma$ is a diagonal matrix of size $p \times p$, and $V$ is an orthogonal matrix of size $n \times p$. If we take a limited of the the projection matrices in the form $A_k = \sum_{i=1}^k\sigma_iu_iv_i^T$ the resulting matrix is called the optimal rank-k approximation of the original matrix. ~\cite{LecturePCA}. In order to project the data into principal component space we simply right multiply our original data matrix by V.
% paragraph singular_value_decomposition (end)
\paragraph{Random Projections} % (fold)
\label{par:random_projections}
An important implication of the Johnson-Lindenstauss lemma is that if one projects the data matrix using a matrix of orthogonal vectors then distances are nearly preserved. Orthogonalization is a costly task, which often defeats the purpose of performing random projections to increase speed performances. Fortunately, it has been shown that with high dimensional spaces there is a high chance that two vectors are nearly orthogonal, and thus it has been shown that by generating random matrices and projecting down to a lower dimensional space using the random matrices one can preserve distances ~\cite{sulic2010dimensionality}. Let k be the dimension of the space we're projecting down to. We used the form of random projections developed by Achlioptas in the form:
	\begin{equation}
		r_{ij} = \frac{\sqrt{3}}{\sqrt{k}} \times \left\{
			\begin{array}{ll}
				+1  & \mbox{with probability } \frac{1}{6} \\
				+0  & \mbox{with probability } \frac{2}{3} \\
				-1  & \mbox{with probability } \frac{1}{6}
			\end{array}
		\right.
	\end{equation} ~\cite{achlioptas2001database}
% paragraph random_projections (end)